\newcommand{\titulus}{\dies{Die 10. Ianuarii.}
\nomenFesti{Die Quinta infra Octavam Epiphaniæ.}}
\newcommand{\postoctavam}{Post octavam}
\newcommand{\sinematutinum}{Sine Matutinum}
\newcommand{\sinelaudes}{Sine Laudes}
\newcommand{\vesperas}{\vspace{1mm}

\pars{Psalmus 1.} \scriptura{\textbf{H76}}

\vspace{-4mm}

\antiphona{II D}{temporalia/ant-anteluciferum.gtex}

\vspace{-2mm}

\scriptura{Ps. 109}

\vspace{-2mm}

\initiumpsalmi{temporalia/ps109-initium-ii-D-auto.gtex}

\vspace{-1.5mm}

\input{temporalia/ps109-ii-D.tex} \Abardot{}

\vfill
\pagebreak

\pars{Psalmus 2.} \scriptura{\textbf{H72}}

\vspace{-4mm}

\antiphona{I g\textsuperscript{2}}{temporalia/ant-venitlumentuum.gtex}

\scriptura{Ps. 110}

\initiumpsalmi{temporalia/ps110-initium-i-g2-auto.gtex}

\input{temporalia/ps110-i-g2.tex} \Abardot{}

\vfill
\pagebreak

\pars{Psalmus 3.} \scriptura{\textbf{H76}}

\vspace{-4mm}

\antiphona{I g\textsuperscript{3}}{temporalia/ant-apertisthesauris.gtex}

\scriptura{Ps. 111}

\initiumpsalmi{temporalia/ps111-initium-i-g3-auto.gtex}

\input{temporalia/ps111-i-g3.tex} \Abardot{}

\vfill
\pagebreak

\pars{Psalmus 4.} \scriptura{\textbf{H76}}

\vspace{-4mm}

\antiphona{IV E}{temporalia/ant-mariaetflumina.gtex}

\scriptura{Ps. 112}

\initiumpsalmi{temporalia/ps112-initium-iv-E-auto.gtex}

\input{temporalia/ps112-iv-E.tex} \Abardot{}

\vfill
\pagebreak

\pars{Psalmus 5.} \scriptura{\textbf{H77}}

\vspace{-4mm}

\antiphona{VII c\textsuperscript{2}}{temporalia/ant-stellaista.gtex}

\vspace{-2mm}

\scriptura{Ps. 113}

\vspace{-2mm}

\initiumpsalmi{temporalia/ps113-initium-vii-c2-auto.gtex}

\input{temporalia/ps113-vii-c2.tex}

\vspace{-5mm}

\antiphona{}{temporalia/ant-stellaista.gtex} % repeat the antiphon - new page

\vfill
\pagebreak}
\newcommand{\capitulum}{\pars{Capitulum.} \scriptura{Is. 60, 1}

\cuminitiali{}{temporalia/capitulum-Surge.gtex}}
\newcommand{\responsoriumbrevevesp}{\pars{Responsorium breve.}

\cuminitiali{VI}{temporalia/resp-omnesdesaba.gtex}}
\newcommand{\hymnusvesperas}{\pars{Hymnus.}

\cuminitiali{III}{temporalia/hym-HostisHerodes.gtex}}
\newcommand{\vespversus}{\pars{Versus.} \scriptura{Ps. 71, 10}

\sineinitiali{temporalia/versus-reges-communis.gtex}}
\newcommand{\magnificat}{\pars{Canticum B. Mariæ V.} \scriptura{Is. 60, 6}

\vspace{-4mm}

{
\grechangedim{interwordspacetext}{0.18 cm plus 0.15 cm minus 0.05 cm}{scalable}%
\antiphona{VIII a}{temporalia/ant-omnesdesaba.gtex}
\grechangedim{interwordspacetext}{0.22 cm plus 0.15 cm minus 0.05 cm}{scalable}%
}

\vspace{-2mm}

\scriptura{Lc. 1, 46-55}

\vspace{-2mm}

\cantusSineNeumas
\initiumpsalmi{temporalia/magnificat-initium-viii-a.gtex}

\vspace{-1.5mm}

\input{temporalia/magnificat-viii-a.tex} \Abardot{}}
\newcommand{\oratioVesperas}{\cuminitiali{}{temporalia/oratioepiphaniae.gtex}}
\include{feria}
